---
title: "Shared Individual Differences Data Cleaning"
author: "Elif Celikors"
date: "2024-05-04"
output: pdf_document
---

Before running this script, set working directory to the "Source File Location"
```{r packages, include = FALSE}
library(tidyverse)
```

DATA CLEANING AND WRANGLING

In the following chunk of code, we exclude subjects who have incorrectly responded to the validation question (attention check) and whose ratings of the same images had a correlation coefficient less than 0.7 (reliability check).

```{r cleaning_excludeSubjects, include = FALSE}
raw <- data.frame(raw <- data.frame(read.csv( "data/SID_rawData.csv"), stringsAsFactors = FALSE), stringsAsFactors = FALSE)
raw <- dplyr::filter(raw, raw$batch!="guessing 12") #ppl in this batch might be taking this study for the second time, so we are eliminating it just in case.. 

# add subject ID column                                                                  
ss_raw = nrow(raw) # sample size
subject_id <- data.frame(subjectID=seq(1:ss_raw))
raw_subjID <- raw %>% dplyr::mutate(subject_ID = c(seq(ss_raw)), .before=Q303)

#############################
##### validation check ######
#############################
remove = vector() # initiate the vector that will hold the subject IDs for pps to be removed

# identify the subjects who didn't pass the attention check question 
remove_no = 1
for (i in 1:ss_raw) {
  if (is.na(raw_subjID$Art.background_4[i]) | raw_subjID$Art.background_4[i] != 0) {
    remove[remove_no] = subject_id[i,] 
    remove_no = remove_no+1}}

##############################
##### reliability check ######
##############################

# extract repeated images
pleasure_v1 <- raw_subjID[, c(102:104,120:122,105:107,12:14,129:131,132:134,6:8,75:77)]
pleasure_v2 <- raw_subjID[, c(153:176)]

remove_cor = vector()
remove_diff = vector()
remove_no_cor = 1
remove_no_diff = 1
reliability_metrics <- array(dim = c(ss_raw,3)) 

for (k in 1:ss_raw) {
  cor <- cor.test(as.numeric(pleasure_v1[k,c(1,4,7,10,13,16,19,22)]),
                  as.numeric(pleasure_v2[k,c(1,4,7,10,13,16,19,22)]), na.rm=T)
  diff <- abs(as.numeric(pleasure_v1[k,c(1,4,7,10,13,16,19,22)]) -
                as.numeric(pleasure_v2[k,c(1,4,7,10,13,16,19,22)]))
  reliability_metrics[k,] <- c(cor$estimate, cor$p.value, sum(diff, na.rm=T))
  
  if (cor$estimate < 0.7 | is.na(cor$estimate)){
    remove_cor[remove_no_cor] = subject_id[k,]
    remove_no_cor = remove_no_cor +1}
  if (sum(diff, na.rm=T) > 8.7) {
    remove_diff[remove_no_diff] = subject_id[k,] 
    remove_no_diff = remove_no_diff + 1}
  }

reliability_metrics <- data.frame(reliability_metrics)
colnames(reliability_metrics) <- c("estimate","p_value","difference")

oneSD_estimate = mean(reliability_metrics$estimate, na.rm=T)-sd(reliability_metrics$estimate, na.rm=T) # 0.64

removed_estimate <- reliability_metrics %>% filter(estimate > oneSD_estimate | is.na(estimate))
removed_diff <- reliability_metrics %>% filter(difference < oneSD_diff)
removed_union <- reliability_metrics %>% 
  filter(!is.na(estimate)) %>% filter(estimate > 0.7 | difference < 8.7)
removed_intersect <- reliability_metrics %>% 
  filter(!is.na(estimate)) %>%  filter(estimate > 0.7 & difference < 8.7)

remove_intersect <- intersect(remove_cor, remove)  
remove_union <- union(remove_cor, remove)
raw_clean <- raw_subjID %>% 
  slice(-remove_union) %>% # remove the bad apples
  dplyr::select(-"Art.background_4", -"RandomID") # remove attn check & randomID columns

hist(reliability_metrics$estimate)
ss = ss_raw-length(remove_union) # update subject number (after removing bad apples) # 368 pp
```

```{r excluded_pps}
pv1 <- raw_subjID[, c(102,120,105,12,129,132,6,75)] %>% slice(remove_cor) %>% 
  mutate(subj_no = 1:67)
pv2 <- raw_subjID[, c(153,156,159,162,165,168,171,174)] %>% slice(remove_cor) %>% 
  mutate(subj_no = 1:67)
pv12 <- merge(pv1, pv2) %>% 
  slice(i) %>%select(-subj_no) %>% t() %>% data.frame() %>% 
  mutate(group = c(rep("first",8), rep("second",8))) %>% 
  mutate(image = rep(c(1:8),2)) %>% rename(rating = 1)
ggplot(pv12, aes(group, rating)) + geom_point() + geom_line(aes(group =image))
```

The following chunk does the following:
- Recodes answers to art background such that we can perform statistical analyses on them.
- Creates a new composite variable ("art_total) for art background. 
- Calculates the personality traits
- Changes variable names
- Creates binary art_background and personality variables (high/low)
```{r cleaning_recodeVariables, include = FALSE}
# re-code art questions
raw_clean$Art.background.2_1[raw_clean$Art.background.2_1=="week"] <- 6 
raw_clean$Art.background.2_1[raw_clean$Art.background.2_1=="month"] <- 5
raw_clean$Art.background.2_1[raw_clean$Art.background.2_1=="2 months"] <- 4
raw_clean$Art.background.2_1[raw_clean$Art.background.2_1=="6 months"] <- 3
raw_clean$Art.background.2_1[raw_clean$Art.background.2_1=="Year"] <- 2
raw_clean$Art.background.2_1[raw_clean$Art.background.2_1=="Almost never"] <- 1

raw_clean$Art.background.2_2[raw_clean$Art.background.2_2=="week"] <- 6
raw_clean$Art.background.2_2[raw_clean$Art.background.2_2=="month"] <- 5
raw_clean$Art.background.2_2[raw_clean$Art.background.2_2=="2 months"] <- 4
raw_clean$Art.background.2_2[raw_clean$Art.background.2_2=="6 months"] <- 3
raw_clean$Art.background.2_2[raw_clean$Art.background.2_2=="Year"] <- 2
raw_clean$Art.background.2_2[raw_clean$Art.background.2_2=="Almost never"] <- 1

# re-code personality questions
row_start =  which(colnames(raw_clean)=="Personality_1")
row_end =  which(colnames(raw_clean)=="Personality_10")

for(x in row_start:row_end) {
  for(y in 1:ss) {
    if (raw_clean[y,x] == "Disagree strongly") {raw_clean[y,x] = 1}
    if (raw_clean[y,x] == "Disagree moderately") {raw_clean[y,x] = 2}
    if (raw_clean[y,x] == "Disagree a little") {raw_clean[y,x] = 3}
    if (raw_clean[y,x] == "Neither agree nor disagree") {raw_clean[y,x] = 4}
    if (raw_clean[y,x] == "Agree a little") {raw_clean[y,x] = 5}
    if (raw_clean[y,x] == "Agree moderately") {raw_clean[y,x] = 6}
    if (raw_clean[y,x] == "Agree strongly") {raw_clean[y,x] = 7}}}

# create a new variable 'art_total' variable that reflects the cumulative art background
art_total = as.numeric(raw_clean$Art.background_1)+as.numeric(raw_clean$Art.background_2)+
         as.numeric(raw_clean$Art.background_3)+as.numeric(raw_clean$Art.background_5)+
         as.numeric(raw_clean$Art.background_6)+as.numeric(raw_clean$Art.background_7)+
         as.numeric(raw_clean$Art.background.2_1)+as.numeric(raw_clean$Art.background.2_2)

# create a new var 'art_binary', which is just a categorical version of art_total
art_binary = if_else((art_total) >= 10, "high", "low")

# calculate personality scores and create new variables for personality types
personality <- matrix(as.numeric(unlist(raw_clean[, row_start:row_end])), nrow=nrow(raw_clean), ncol=length(row_start:row_end))
extra <- (personality[,1] + (8 - personality[,6]))/2
agree <- (personality[,7] + (8 - personality[,2]))/2
cons <- (personality[,3] + (8 - personality[,8]))/2
emo <- (personality[,9] + (8 - personality[,4]))/2
open <- (personality[,5] + (8 - personality[,10]))/2

# add new variables to the raw_clean df and fix some column names
raw_final <- raw_clean %>% 
  mutate(art_total = art_total, .after=Art.background.2_2) %>% 
  mutate(art_binary = art_binary, .after=Art.background.2_2) %>% 
  mutate(extra = extra, .after=Personality_10) %>% 
  mutate(agree = agree, .after=Personality_10) %>% 
  mutate(cons = cons, .after=Personality_10) %>% 
  mutate(emo = emo, .after=Personality_10) %>% 
  mutate(open = open, .after=Personality_10) %>% 
  mutate(extra_bi = if_else(extra >= 4, "extravert", "introvert"), .after=Personality_10) %>% 
  mutate(agree_bi = if_else(agree >= 5, "agreeable", "not_agreeable"), .after=Personality_10) %>% 
  mutate(cons_bi = if_else(cons >= 6, "cons", "not_cons"), .after=Personality_10) %>% 
  mutate(emo_bi = if_else(emo >= 5, "stable", "not_stable"), .after=Personality_10) %>% 
  mutate(open_bi = if_else(open >= 5, "open", "not_open"), .after=Personality_10) %>% 
  rename(age=Q303, gender=Q1, race=Q305, education=Q2, occupation=Q3, cision=Q314) %>% 
  mutate(age_binary = if_else(as.numeric((raw_clean$Q303)) >= 40, "old", "young"), .after=age) 
```

In the following lines of codes, we finalize the data frame that will be used in analyses ("self").
The originally imported data frame contains data on people's prediction of lay people's and art experts' ratings of the images (We don't use this data in this script).

We export these data as SID_self_ratings.csv, which will be the main input of our analyses in "SID_analysis.Rmd"
```{r dataframes, include = FALSE}
pleasure <- raw_final %>% dplyr::select(-1:-2) %>% dplyr ::mutate(ID = c(1:nrow(raw_final)))  # df containing ALL cleaned data
demog_start =  which(colnames(pleasure)=="subject_ID")
self_demog <- cbind(data.frame((pleasure[seq(1, length(pleasure), 3)]))[,1:50],
               pleasure[,demog_start:ncol(pleasure)]) %>% na.omit()
self <- self_demog[,1:50] %>% t() %>% unlist() %>% as.numeric() %>% matrix(nrow = 50)

write.csv(self, "data/SID_selfRatings_noExclusion.csv")
```

